Motion planning for assessing accessibility of protein tunnels

### 2017-09-10 paper.tex
joined paragraphs in the section IV-D

The third modification is the utilization of another metric during the expansion procedure (line~\ref{alg::expand:a} in Alg.~\ref{alg::expand}).
This metric is denoted as $\da(\cdot,\cdot)$ and it is referred to as atom-based metric in the rest of the paper.
To evaluate $\da(q_1,q_2)$, the absolute positions of the atoms of the ligand defined by $q_1$ and $q_2$ are computed.
The minimal 3D Euclidean distance from the first set of atoms (defined by $q_1$) to the second set of atoms (defined by $q_2$) is the value of 
$\da(q_1,q_2)$.
By computing the atom-based metric using the absolute positions of atoms, this metric considers the shape of the ligands, which
is useful when multiple conformations are utilized.
By employing this metric in the expansion procedure, the tree is expanded by such a new configuration, whose atoms maximally approach
the atoms of the configuration $\qrand$.
We observed that this leads to a better construction of the configuration tree inside the proteins and it increases the probability
of reaching the active site.

@@

In the expansion step, each conformation from $\L$ is tested in order to approach $\qrand$.
By using more conformations, there is a higher chance that at least one of them can expand the tree towards the random sample $\qrand$.
On the other hand, using a large number of conformations also increases the time complexity of the expansion step.
Selection of a suitable set of conformations $\L$ is therefore crucial.
Depending on the ligand, some conformations can be considered as more packed i.e., the atoms in such conformations are closer to each other, but 
the atoms can also form a more elongated shape (Fig.~\ref{fig::m040c}).

@@

From the motion planning point of view, both types of conformations are useful.
The longer conformations can better fit in a narrow passage, while the packed conformations can be better rotated at a given position.
In the narrow parts of the tunnel, the tree can be extended by the longer conformations, while in the wider regions, also the
packed conformations can be used.

>>>>

The third modification is the utilization of another metric during the expansion procedure (line~\ref{alg::expand:a} in Alg.~\ref{alg::expand}).
This metric is denoted as $\da(\cdot,\cdot)$ and it is referred to as atom-based metric in the rest of the paper.
To evaluate $\da(q_1,q_2)$, the absolute positions of the atoms of the ligand defined by $q_1$ and $q_2$ are computed.
The minimal 3D Euclidean distance from the first set of atoms (defined by $q_1$) to the second set of atoms (defined by $q_2$) is the value of 
$\da(q_1,q_2)$.
By computing the atom-based metric using the absolute positions of atoms, this metric considers the shape of the ligands, which
is useful when multiple conformations are utilized.
This metric ensures that the tree is expanded by such configurations, whose atoms maximally approach
the atoms of the configuration $\qrand$.
We observed that this leads to a better construction of the configuration tree inside the proteins and it increases the probability
of reaching the active site.

@@

In the expansion step, each conformation from $\L$ is tested in order to approach $\qrand$.
By using more conformations, there is a higher chance that at least one of them can expand the tree towards the random sample $\qrand$.
On the other hand, using a large number of conformations also increases the time complexity of the expansion step.
Selection of a suitable set of conformations $\L$ is therefore crucial.
Depending on the ligand, some conformations can be considered as more packed i.e., the atoms in such conformations are closer to each other, but 
the atoms can also form a more elongated shape (Fig.~\ref{fig::m040c}).
From the motion planning point of view, both types of conformations are useful.
The longer conformations can better fit in a narrow passage, while the packed conformations can be better rotated at a given position.
In the narrow parts of the tunnel, the tree can be extended by the longer conformations, while in the wider regions, also the
packed conformations can be used.

@@
